Modelling the emergence of whisker barrels

### 2020-06-12 paper/briefpaper/brief.tex
Updated figure
Figure improvements

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}. \textbf{B} The strengths of interaction
      $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
      projections by the lengths of green and blue arrows respectively, assuming
      that similar fields aligned to the posterior-anterior and medial-lateral
      axes in the ventroposterior medial nucleus of the thalamus are sampled at
      the locations of putative barreloid centers (reconstructed from
      \citealp{haidarliu_size_2001}). \textbf{C} Simulation results for parameters
      \cmnt{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
      $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours indicate the thalamic
      projection for which the connection density is maximal and black lines
      delineate boundaries (see Movie
      S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from
      simulation approaching that obtained from \cmnt{real} barrels in \textbf{A} (dotted
      line); black squares \cmnt{give a} measure \cmnt{of} the correspondence
      between the real and
      simulated barrel shapes, $\eta$ (the sum of differences in
      area; units \cmnt{mm$^2$});
      \cmnt{grey hexagons show the measure of localization, $\omega =
        \oiint_{S} \left( \mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i\right) \mathrm{d}S$. }
      \textbf{E} \cmnt{The localization measure plotted across the domain
        shows that the structure in the connection density which has developed
        by $t=30000$ is largely absent at $t=1000$. The
        colour map
        indicates the values of  $\mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i$. Overlaid
        contours show $c_i > 0.95 \mathrm{max}_i(c_i)$.} All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

\cmnt{We performed a sensitivity analysis to determine if the quality of the
  pattern was sensitive to any of the following inputs: i)~The angle and
  magnitude of each of the two guidance fields (Fig.\,\ref{fig:main}A);
  ii)~the magnitude, offset and characteristic length scale of the noise
  applied to $a_i$ at $t=0$; and iii)~the magnitude of each of the interaction
  parameters, $\gamma_{i,j}$. We analysed the effect on the three pattern
  metrics, $\delta$, $\eta$ and $\omega$ evaluated after 30000 simulation
  steps. First, we conducted 10 runs of the simulation to evaluate the mean
  and standard deviation (as a result of the different random initial
  conditions for $a_i$) of the three metrics in the default model
  (Fig.\,\ref{fig:main}C--E) which were $\delta=0.089\pm{0.004}$,
  $\eta=0.531\pm{0.005}$ and $\omega=0.2165\pm{0.0001}$). These results are
  not strongly affected by the random initial conditions for $a_i$ but give a
  baseline from which to evaluate whether changes in the other inputs have a
  statistically significant effect.}

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig3.png}
  \captionof{figure}{Guidance
    fields and emergent barrel pattern in a Fgf8 misexpression experiment
    (c.f. \citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
    $\rho_1$ from Fig.\,\ref{fig:main}A at the join. \cmnt{The model
      parameters match those in Fig.\,\ref{fig:main}C. Scale
      bars are 1\,mm.}}
  \label{fig:fgf8}
\end{center}

@@

>>>>

\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig1.png}
    \caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
      by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
      measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
      perfect Voronoi tesselation. Right shows the initial distribution of axon
      branching density ($a$) for one thalamocortical projection, and two
      molecular guidance fields ($\rho$), \cmnt{where the domain $S$ has been
        traced from \textbf{A}}. \textbf{B} The strengths of interaction
      $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
      projections by the lengths of green and blue arrows respectively, assuming
      that similar fields aligned to the posterior-anterior and medial-lateral
      axes in the ventroposterior medial nucleus of the thalamus are sampled at
      the locations of putative barreloid centers (reconstructed from
      \citealp{haidarliu_size_2001}, \cmnt{Fig.\,5b}). \textbf{C} Simulation results for parameters
      \cmnt{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
      $\epsilon=1.2$} and $\delta{t}=0.0001$. Colours indicate the thalamic
      projection for which the connection density is maximal and black lines
      delineate boundaries (see Movie
      S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from
      simulation approaching that obtained from \cmnt{real} barrels in \textbf{A} (dotted
      line); black squares \cmnt{give a} measure \cmnt{of} the correspondence
      between the real and
      simulated barrel shapes, $\eta$ (the sum of differences in
      area; units \cmnt{mm$^2$});
      \cmnt{grey hexagons show the measure of localization, $\omega =
        \oiint_{S} \left( \mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i\right) \mathrm{d}S$. }
      \textbf{E} \cmnt{The localization measure plotted across the domain
        shows that the structure in the connection density which has developed
        by $t=30000$ is largely absent at $t=1000$. The
        colour map
        indicates the values of  $\mathrm{max}_i(c_i)/\sum_{i=1}^{N} c_i$. Overlaid
        contours show $c_i > 0.95 \mathrm{max}_i(c_i)$.} All scale bars 1\,mm.}
    \label{fig:main}
  \end{fullwidth}
\end{figure}

@@

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig3.png}
    \caption{\cmnt{Sensitivity analysis. Column \textbf{A} shows...}}
    \label{fig:sens}
  \end{fullwidth}
\end{figure}

\cmnt{We performed a sensitivity analysis to determine if the quality of the
  pattern was affected by perturbations to any of the following inputs:
%
  i)~the magnitude and offset of the noise applied to $a_i$ at $t=0$;
%
  ii)~random noise applied to the interaction parameters, $\gamma_{i,j}$;
%
  iii)~random noise (of various length scales) applied to the guidance fields;
%
  and
%
  iv)~The angle and magnitude of one of the guidance fields, ($\rho_1$;
  Fig.\,\ref{fig:main}A).
%
  We analysed the effect on the three pattern metrics, $\delta$ (the Honda
  Voronoi metric), $\eta$ (the pattern-match metric) and $\omega$ (which
  measures localization of connections, $c_i$) evaluated after 30000
  simulation steps.}

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The results (where deviations occur as a
  result of the different random initial conditions for $a_i$) were
  $\delta=0.089\pm{0.004}$, $\eta=113.5\pm{1.2}$ and
  $\omega=0.2165\pm{0.0001}$. None of the three metrics were strongly affected
  by the random initial conditions for $a_i$. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we changed the initial condition for $a_i$, changing the
  parameters of the generating uniform distribution to set each hex to
  $0.4+{U}(0,0.4)$. We ran this system 10 times and obtain the result
  $\delta=0.0\pm{0.000}$, $\eta=100\pm{0}$ and $\omega=0.2ish\pm{0.0000}$. A
  t-test demonstrates that this is ????. A final test of a noise-free initial
  condition with $a_i=0.2$ for every hex also ????.}

\cmnt{Fig\,\ref{fig:sens}A shows the results for perturbations ii) to iv). The
  first column shows the results for the three metrics where the interaction
  parameters $\gamma_{i,j}$ are replaced by $\gamma_{i,j}'$ according to
  $\gamma_{i,j}' = \gamma_{i,j} + U(0,4\nu_\gamma)$, where $\nu_\gamma$ is the
  chosen magnitude of the noise (the proportion of the full range of
  $\gamma_{i,j}$, which is 4). The Voronoi nature of the pattern ($\delta$)
  and the localization of the fields are not strongly affected by interaction
  parameter noise, but the pattern metric, $\eta$ shows a... ADD SUB GRAPH.}

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png}
  \captionof{figure}{Guidance
    fields and emergent barrel pattern in a Fgf8 misexpression experiment
    (c.f. \citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
    $\rho_1$ from Fig.\,\ref{fig:main}A at the join. \cmnt{The model
      parameters match those in Fig.\,\ref{fig:main}C. Scale
      bars are 1\,mm.}}
  \label{fig:fgf8}
\end{center}

@@

\cmnt{Add a description of $\eta$, the pattern-matching measure, here.}
